Response to reviewers

### 2022-02-08 paper/paper.Rmd
addressing the first three of the reviewers comments

This paper demonstrates the steps of cleaning data, and documents the process, as recommended by @HuebnerMariannePhD2016Asat.  They emphasize that making the data cleaning process accountable and transparent is imperative and essential for the integrity of downstream statistical analyses and model building. Data cleaning can be considered to be a part of what is called "initial data analysis" (IDA) [@Chatfield1985TIEo]. In IDA one would also explore the data, especially to check if the data is consistent with assumptions required for modeling. This is also related to exploratory data analysis (EDA), coined by @tukey with a focus on learning from data. EDA can be considered to encompass IDA. @DasuTamraparni2003Edma say that data cleaning and exploration, without naming it as IDA, is a difficult task and consumes 80% of the data mining task.

>>>>

This paper demonstrates the steps of cleaning data, and documents the process, as recommended by @HuebnerMariannePhD2016Asat.  They emphasize that making the data cleaning process accountable and transparent is imperative and essential for the integrity of downstream statistical analyses and model building. Clean data often then goes through an "initial data analysis" (IDA) [@Chatfield1985TIEo], where one would  summarize and scrutinize the data, especially to check if the data is consistent with assumptions required for modeling. This stage is related to exploratory data analysis (EDA), coined by @tukey with a focus on learning from data. EDA can be considered to encompass IDA. In practice the three stages of cleaning, summarizing and exploring are cyclical, that one often needs to do more cleaning after scrutinizing. @DasuTamraparni2003Edma say that data cleaning and exploration is a difficult task and typically consumes a large percentage of the time spent in analyzing data.

### 2022-02-08 paper/paper.tex
addressing the first three of the reviewers comments

This paper demonstrates the steps of cleaning data, and documents the process, as recommended by Huebner, Vach, and Cessie (2016). They emphasize that making the data cleaning process accountable and transparent is imperative and essential for the integrity of downstream statistical analyses and model building. Data cleaning can be considered to be a part of what is called ``initial data analysis'' (IDA) (Chatfield 1985). In IDA one would also explore the data, especially to check if the data is consistent with assumptions required for modeling. This is also related to exploratory data analysis (EDA), coined by Tukey (1977) with a focus on learning from data. EDA can be considered to encompass IDA. Dasu and Johnson (2003) say that data cleaning and exploration, without naming it as IDA, is a difficult task and consumes 80\% of the data mining task.

>>>>

This paper demonstrates the steps of cleaning data, and documents the process, as recommended by Huebner, Vach, and Cessie (2016). They emphasize that making the data cleaning process accountable and transparent is imperative and essential for the integrity of downstream statistical analyses and model building. Clean data often then goes through an ``initial data analysis'' (IDA) (Chatfield 1985), where one would summarize and scrutinize the data, especially to check if the data is consistent with assumptions required for modeling. This stage is related to exploratory data analysis (EDA), coined by Tukey (1977) with a focus on learning from data. EDA can be considered to encompass IDA. In practice the three stages of cleaning, summarizing and exploring are cyclical, that one often needs to do more cleaning after scrutinizing. Dasu and Johnson (2003) say that data cleaning and exploration is a difficult task and typically consumes a large percentage of the time spent in analyzing data.

### 2022-02-08 response/response1.Rmd
abstract and title revised
addressing the first three of the reviewers comments

\begin{description}
\item[Reviewer 1:] \textcolor{violet}{How is this manuscript relevant for teachers and/or students in statistics and data science?}
\item[Reviewer 3:] \textcolor{violet}{The authors prominently cite (Chatfield 1985) for the definition of the term “IDA”. However, Chatfield fairly explicitly defines IDA to be a data summarizing and scrutinizing process; not a cleaning, scrubbing, or munging process. It seems curious to me that the whole paper is framed as being “IDA” based on the author’s unsupported statement that data cleaning should be considered party of IDA.}
\item[Reviewer 3:] \textcolor{violet}{My suggestion is that the authors reconfigure this paper to be presented as a pure case study. Ibelieve the work that has been done is valuable: the data cleaning process is often messy andunplanned, so a case study like this on a popular dataset would provide an excellent educational resource.}
\end{description}

Supporting information for the lack of data cleaning in papers.

>>>>

\begin{description}
\item[Reviewer 1:] \textcolor{violet}{How is this manuscript relevant for teachers and/or students in statistics and data science?}

The introduction has been re-written with an emphasis on how this work should be interesting for teachers and students of data science and statistics.

\item[Reviewer 3:] \textcolor{violet}{The authors prominently cite (Chatfield 1985) for the definition of the term “IDA”. However, Chatfield fairly explicitly defines IDA to be a data summarizing and scrutinizing process; not a cleaning, scrubbing, or munging process. It seems curious to me that the whole paper is framed as being “IDA” based on the author’s unsupported statement that data cleaning should be considered party of IDA.}

Yes, there is grey area in these three activities. Thanks for pointing out Chatfield's original viewpoint, which differs from Huebner et al's. We have revised this paragraph to de-emphasize cleaning as being part of IDA. We have kept the explanation of the terminology of IDA and EDA because we think this is important for clarifying for teaching purposes.

\item[Reviewer 3:] \textcolor{violet}{My suggestion is that the authors reconfigure this paper to be presented as a pure case study. I believe the work that has been done is valuable: the data cleaning process is often messy and unplanned, so a case study like this on a popular dataset would provide an excellent educational resource.}

We have kept the case study frame of mind but have re-cast the paper so that it focuses on the importance of this type of activity for teaching of statistics and data science. 
\end{description}
